---
title: "Create_graphs_for_NVI"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Create_graphs_for_NVI}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

You can create graphs and plots in accord with NVI's graphical profile when using ggplot2 with the theme_NVI and the palette_NVI. Here we use the built in data set iris

```{r setup}
```

Make a scatter plot with distribution of spetal_length per iris species. First we use the default theme in ggplot2, which is theme_grey.
```{r} 
library(ggplot2)
# Scatter plot
ggplot(iris, aes(Sepal.Length, Sepal.Width)) +
  geom_point(aes(color = Species)) +
  theme(legend.position = "right") 
```

Then we would like to make the scatter plot in accord with the graphical profile. We use the theme_NVI and palette_graph that is in the package NVIpretty. First attach the package.

```{r echo = FALSE}
library(NVIpretty)
```

You can add theme_NVI in the ggplot function as another statement. theme_NVI removes the background, set the colour for the axis marks and the horizontal support lines. Using palette_graph sets the colours to the colours in the graphical profile.
```{r} 
# Scatter plot
ggplot(iris, aes(Sepal.Length, Sepal.Width)) +
  geom_point(aes(color = Species)) +
  theme(legend.position = "right")  +
  theme_NVI() +
  scale_colour_manual(values = palette_graph)
```

Instead of setting the theme in all the code, you may change the default theme for the session to theme_NVI.  
```{r}
theme_set(theme_NVI())
```

Box plot
```{r} 
ggplot(iris, aes(Species, Sepal.Length)) +
  geom_boxplot(aes(fill = Species)) +
  theme(legend.position = "right") + 
  scale_fill_manual(values = palette_graph)
```

# Change colors
ggplot(df, aes(x=weight)) + 
  geom_histogram(bins=10, color="black", fill=palette_NVI )

# Change histogram plot line colors by groups
ggplot(df, aes(x=weight, color=sex)) +
  geom_histogram(fill=palette_NVI)
