---
title: "NVI colour palettes"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{NVI colour palettes}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r, echo = FALSE}
library(ggplot2)

set_name_vector <- function(x) {
  new_names <- x
  new_names[which(names(x) != "")] <- names(x[which(names(x) != "")])
  x <- stats::setNames(x, new_names)
  return(x)
}

display_palett <- function(palette, reverse_colours = FALSE, title = NULL) {
  if (is.null(title)) {title = deparse(substitute(palette))}
  if (isTRUE(reverse_colours)) {palette <- rev(palette)}
  # Use colour codes as names if names are not given
  palette <- set_name_vector(palette)
  # create data set with the colour codes to plot
  colorKey = data.frame(colorName = names(palette))
  # plot with ggplot, use the clours in the palette
  ggplot(data = colorKey, aes(x = 1, y = 1:nrow(colorKey), fill = colorName, label = colorName)) +
    geom_tile() +
    scale_fill_manual(values = palette) +
    theme_void() +
    theme(legend.position = "none") +
    geom_text() +
    ggtitle(title) +
    theme(plot.title = element_text(hjust = 0.5))
}

# Function for plotting colors side-by-side
# display_palett <- function(palette, border = "light gray", ...){
#   title <- deparse(substitute(palette))
#   n <- length(palette)
#   plot(0, 0, type="n", xlim = c(0, 1), ylim = c(0, 1),
#        axes = FALSE, main=title, xlab = "", ylab = "", ...)
#   rect(0, 0:(n-1)/n, 1, 1:n/n, col = palette, border = border)
#   # rect(0:(n-1)/n, 0, 1:n/n, 1, col = palette, border = border)
# }
```

The graphical profile for NVI is published on the NVI intranet. The different colour palettes in the NVI graphical profile is displayed below. The palettes are collected in the R-package NVIpretty.

## The NVI profile colours

The NVI profile colours are collected in the palette palette_NVI.

```{r fig.width = 5, echo = FALSE}
library(NVIpretty)

display_palett(palette_NVI, reverse_colours = TRUE)
```

## The NVI colours for graphs

The NVI profile has 15 different colours for use in graphs. These are collected in the palette: "palette_graph". The colours should be used in the order they are in the graph.

```{r fig.width = 5, fig.height = 4, echo = FALSE}
names(palette_graph) <- c("Jord", "Luft", "Vann", "Svart", "Lys_jord", 
                          "Mørk_luft", "Lys_vann", "Mat", "Lys_mat", "Gul", 
                          "Lys_gul", "Lilla", "Lys_lilla", "Orange", "Lys_orange")
display_palett(palette_graph, reverse_colours = TRUE)
```

## The NVI colours for gradients

There are six different colour gradients based on the NVI profile colours. Within each gradient, there are six different colours. These are intended for choropleth maps and can also be used in graphs.

```{r fig.width = 7, fig.height = 5, echo = FALSE}
library(grid)
names(palette_gradient_jord)[3] <- "Jord"
plot_jord <- display_palett(palette_gradient_jord,
                            reverse_colours = TRUE,
                            title = paste("palette_gradient_jord", "palette_gradient_earth", 
                                          "palette_gradient_green", sep = "\n"))
names(palette_gradient_luft)[1] <- "Luft"
plot_luft <- display_palett(palette_gradient_luft,
                            reverse_colours = TRUE,
                            title = paste("palette_gradient_luft", "palette_gradient_air", 
                                          "palette_gradient_lightblue", sep = "\n"))
names(palette_gradient_vann)[5] <- "Vann"
plot_vann <- display_palett(palette_gradient_vann,
                            reverse_colours = TRUE,
                            title = paste("palette_gradient_vann", "palette_gradient_water",
                                          "palette_gradient_darkblue", sep = "\n"))
names(palette_gradient_mat)[3] <- "Mat"
plot_mat <- display_palett(palette_gradient_mat,
                           reverse_colours = TRUE,
                           title = paste("palette_gradient_mat", "palette_gradient_food", 
                                         "palette_gradient_red", sep = "\n"))
names(palette_gradient_gul)[3] <- "Gul"
plot_gul <- display_palett(palette_gradient_gul,
                           reverse_colours = TRUE,
                           title = paste("", "palette_gradient_gul", "palette_gradient_yellow", sep = "\n"))
names(palette_gradient_graa)[6] <- "Svart"
plot_graa <- display_palett(palette_gradient_graa,
                            reverse_colours = TRUE,
                            title = paste("", "palette_gradient_graa", "palette_gradient_grey", sep = "\n"))
pushViewport(viewport(layout = grid.layout(2, 3)))
vplayout <- function(x, y) viewport(layout.pos.row = x, layout.pos.col = y)
print(plot_jord, vp = vplayout(1, 1))
print(plot_luft, vp = vplayout(1, 2))
print(plot_vann, vp = vplayout(1, 3))
print(plot_mat, vp = vplayout(2, 1))
print(plot_gul, vp = vplayout(2, 2))
print(plot_graa, vp = vplayout(2, 3))
```

